Figures

### 2019-12-02 figures/07_model-selection.Rmd
color and legend fixes

# gg_line

@@

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line()) +
  ggtitle("TP") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

>>>>

@@

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("black", "red")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank(), 
        legend.position = "none") +
  ggtitle("TN") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("black", "red")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        legend.position = "none") +
  ggtitle("TP") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
